---
title: "uppercase id"
author: "COBBY"
date: "13/03/2022"
output:
  word_document: default
  html_document: default
---

```{r}
library(readr)
```


```{r}
library(Hmisc)
```


```{r}
library(dplyr)
```


```{r}
library(stringr)

```


```{r}
analysisData = read.csv("analysis.csv", stringsAsFactors = T)
```



```{r}
analysisData
```








```{r}
escapeData = read.csv("escapes.csv", stringsAsFactors = T)
```


#Columns Aquaculture.Type contain only one value so they are useless
```{r}
escapeData$Aquaculture.Type <- NULL
```


#replacing unknown in Average.Weight Column(escape.csv) with NA
```{r}
escapeData$Average.Weight[escapeData$Average.Weight == "unknown"] <- NA
```


#replacing unknown in Age Column(escape.csv) with NA
```{r}
escapeData$Age[escapeData$Age == "unknown"] <- NA
```


#replacing NA in Age with the Mean/median
```{r}
escapeData$Age <- impute((escapeData$Age), median)
```

```{r}
escapeData <- escapeData %>% mutate(Age = replace(Age, match("2000524", Escape.ID), "9 months"))
```


#replacing NA in Age with the Mean/median
```{r}
escapeData$Average.Weight <- impute((escapeData$Average.Weight), median)
```


```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000401", Escape.ID), "20 months"))
```


```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000492", Escape.ID), "3 months"))
```


```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000519", Escape.ID), "13 months"))
```


```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000099", Escape.ID), "18 months"))
```


```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000448", Escape.ID), "14 months"))
```


```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("20005111", Escape.ID), "6 months"))
```


```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000442", Escape.ID), "14 months"))
```


```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000086", Escape.ID), "7 months"))
```


```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000516", Escape.ID), "3 months"))
```


```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000175", Escape.ID), "12 months"))
```


```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000521", Escape.ID), "18 months"))
```


```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000512", Escape.ID), "6 months"))
```


```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000524", Escape.ID), "9 months"))
```


```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000355", Escape.ID), "20 months"))
```


```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000347", Escape.ID), "21 months"))
```


```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000352", Escape.ID), "10 months"))
```


```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000382", Escape.ID), "9 months"))
```


```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000131", Escape.ID), "6 months"))
```
```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000131", Escape.ID), "6 months"))

```

```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000363", Escape.ID), "6 months"))
```

```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000399", Escape.ID), "6 months"))

```

```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000363", Escape.ID), "6 months"))

```

```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000397", Escape.ID), "4 months"))
```

```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000484", Escape.ID), "6 months"))
```

```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000364", Escape.ID), "6 months"))
```

```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000078", Escape.ID), "6 months"))
```

```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000339", Escape.ID), "6 months"))

```

```{r}
escapeData <- escapeData%>% mutate(Age = replace(Age, match("2000322", Escape.ID), "6 months"))
```


```{r}
lowerAll <- function (dataset) {
   for ( i in 1:ncol(dataset)) {
       if (class(dataset[,i])=="factor") 
{dataset[,i] <- str_to_lower(dataset[,i])} 
   }
   return(dataset)
}

```



```{r}
escapeData <- lowerAll(escapeData)
analysisData <- lowerAll(analysisData)
```



```{r}
escapePlus <- merge(escapeData, analysisData, by="Site.Name", all=TRUE)
```

```{r}
write.table(escapePlus, file="escapePlus.csv", sep=",")
```

```{r}
library(ggplot2) 
```


#exploratory data analysis on analysisData.csv
```{r}
summary(analysisData$c2)
summary(analysisData$c3)
summary(analysisData$c4)
summary(analysisData$c5)
summary(analysisData$c6)
summary(analysisData$c7)
```


###from the exploratory data analysis (summary) we can tell there is a normal distribution
### because both the mean and the median are close in figures

```{r}
IQR(analysisData$c2)
IQR(analysisData$c3)
IQR(analysisData$c5)
IQR(analysisData$c6)
IQR(analysisData$c7)
```


```{r}
library(ggplot2)
```



```{r}
range(analysisData$c2)
range(analysisData$c3)
range(analysisData$c4)
range(analysisData$c5)
range(analysisData$c6)
range(analysisData$c7)
range(analysisData$year)
```
##the year range spans from 1998 to 2020



```{r}
var(analysisData$c2)
sd(analysisData$c2)

##optional
```


```{r}
p <- ggplot(data=analysisData, aes(x=c2))
p <- p+geom_histogram()
```



```{r}
p
```

```{r}
p <- ggplot(data=analysisData, aes(y=c6))
p <- p+geom_boxplot()
```


```{r}
p
```


#plotting c2 against c3 in analysis.csv
```{r}
p <- ggplot(data=analysisData, 
aes(x=c2, y=c3))
p <- p+geom_point()
p
```



```{r}
cor(analysisData$c2,analysisData$c3)
```
## from the value above we can see c2 and c3 of AnalysisData is correlated 





